### 2014-09-06 related.tex
related

@@

Said et al. \cite{Said:2011} describe a PTA that is also sound albeit not maximal. Similarly to our analysis, Said et al. perform symbolic analysis of the input trace, and then utilize an SMT solver to search for interleaved schedules that establish the presence of data races. Soundsness is guaranteed by their ability to precisely encode the semantics of sequential consistency. ExceptionNULL \cite{Farzan:2012} is another example of a sound PTA without maximality guarantees, where the goal is to detect null dereferences rather than data races.

Serbanuta et al. \cite{SerbanutaCR12} have recently shown that it is possible to build a model that is not only sound but also maximal: Any extension of the model with a new trace renders the model unsound. The theoretical framework created by Serbanuta et al. provides a foundation for different forms of PTA, including data races, but also atomicity, serializability and other properties.

Inspired by this result and closer to \tool\ is the PTA technique of Huang et al. \cite{HuangMR14}, which --- like our technique --- is sound and also maximal, but only under the assumption that local assignments are not modeled. Huang et al.s technique, too, makes use of an SMT solver based on symbolic encoding of the input trace. As part of the encoding, control-flow information is taken into account to enable reorderings that do not violate control dependencies. Still, the two relaxations that \tool\ features, which enable (i) value- rather than dependence-based reasoning about data flow and (ii) consideration of unexplored branches, are strictly outside the scope of Huang et al.'s technique. In Section \ref{sec:eval}, we demonstrate via direct comparison with Huang et al. the dramatic improvement in coverage thanks to these relaxation methods, which we prove to handle in a sound manner.

>>>>

Serbanuta et al. \cite{maximal} have recently shown that it is possible to build a model that is not only sound but also maximal: Any extension of the model with a new trace renders the model unsound. The theoretical framework created by Serbanuta et al. provides a foundation for different forms of PTA, including data races, but also atomicity, serializability and other properties. Serbanuta et al. do not report on any concrete instantiation of their framework.

@@

Said et al. \cite{Said:2011} and Huang et al. \cite{HuangMR14} describe PTAs that are also sound albeit not maximal. Said et al. perform symbolic analysis of the input trace, and then utilize an SMT solver to search for interleaved schedules that establish the presence of data races. Soundsness is guaranteed by their ability to precisely encode the semantics of sequential consistency. 
Inspired by Said et al., Huang et al. present an improvement, whereby control-flow information is encoded into the constraint system so as to relax flow dependencies as long as control dependencies are preserved.
ExceptionNULL \cite{Farzan:2012} is another example of a sound PTA without maximality guarantees, where the goal is to detect null dereferences rather than data races.

\tool\ is similar to Said et al. and Huang et al. in that it also makes use of an SMT solver based on symbolic encoding of the input trace. Still, the two relaxations that \tool\ features, which enable (i) value- rather than dependence-based reasoning about data flow and (ii) consideration of unexplored branches, are strictly outside the scope of both of these techniques. In Section \ref{sec:eval}, we demonstrate via direct comparison with Huang et al. the dramatic improvement in coverage thanks to these relaxation methods, which we prove to handle in a sound manner.
